---
title: "p8105_hw1_fy2297"
output: github_document
---



# Problem 1
## description of the dataset
```{r}
# get dataset using code provided
data("penguins", package = "palmerpenguins")
# make a new dataset without N/A values in flipper length column
penguins_new <- penguins[-c(4,272),]
# calculate the sizes of the new dataset
num_row <- nrow(penguins)
num_col <- ncol(penguins)
# calculate the mean of flipper length
mean_flipper <- mean(penguins_new$flipper_length_mm)
```
The name of the dataset is called penguins, and there are `r num_col` different variables.
The size of the dataset is `r num_col` * `r num_row`, and the mean flipper length is `r mean_flipper`mm.

## scatterplot making
```{r}
# run library first
library(tidyverse)
# name axes for better future use
x_axis <- penguins_new$bill_length_mm
y_axis <- penguins_new$flipper_length_mm
plot = tibble(x = x_axis, y = y_axis)
# make a plot using ggplot
species = penguins_new$species
ggplot(plot,aes(x=x, y=y, color = species))+geom_point()+labs(title = "bill length v.s. flipper length", x = "bill length (mm)",y = "flipper length (mm)")
# save the plot just created
ggsave("bill length v.s. flipper length", plot = last_plot(), device = "pdf")
```

# Problem 2
```{r}
set.seed(1234)
# create four different vectors
normal_vector <- rnorm(10)
logical_vector <- normal_vector>0
character_vector <- vector("character", 10)
factor_vector <- factor(c("small","medium","large","small","medium","large","small","medium","large","small"))
# make a data frame using four vectors
df = tibble (normal_vector, logical_vector, character_vector, factor_vector)
# pull the variables out of the frame
data_norm <- pull(df, var = normal_vector)
data_logical <- pull(df, var = logical_vector)
data_character <- pull(df, var = character_vector)
data_factor <- pull(df, var = factor_vector)
# take the means of each variable (w/o as.numeric)
mean_norm <- mean(data_norm)
mean_logical <- mean(data_logical)
mean_character <- mean(data_character)
mean_factor <- mean(data_factor)
```
when calculating the means of each vector, only normal and logical vector works, but character and factor vectors don't.

```{r eval = FALSE}
data_logical_num = as.numeric(data_logical)
data_character_num = as.numeric(data_character)
data_factor_num = as.numeric(data_factor)
mean_logical_num = mean(data_logical_num)
mean_character_num = mean(data_character_num)
mean_factor_num = mean(data_factor_num)
```
after converting them to "double" type vector, means can be calculated. It explained why it didn't work before b/c R could only take means of "double" and "integer". 



